\chapter{Definitions and abbreviated terms}

\section{Definitions}
\begin{itemize}
    \item \textbf{Total ionizing dose} -- the portion of the energy absorbed by a matter during the whole time of exposure on ionizing radiation. \cite{RadFET_PhD} Expressed in grays (Gy) or rads (Rad). \SI{1}{Gy} = \SI{100}{\rad}.

    \item \textbf{CubeSat} -- a nano-satellite, composed of multiples 10 x 10 x 11.35 cm cubic units, each of a 1.33 kg mass. Frequently build by an university students, for educational and research purposes. \cite{CDS}

    \item \textbf{RadFET} -- common name for specialized, radiation sensitive P-MOSFET transistors used in TID measurements.

    \item \textbf{Low Earth orbit} -- an orbit with an altitude between 180 km and 2000 km. Most scientific and observatory satellites are located at the Low Earth Orbit. \cite{NASA_orbits}

    \item \textbf{Dosimeter} -- a sensor that measures exposure to ionising radiation.

    \item \textbf{PW-Sat2} -- second CubeSat, undergo building on Warsaw University of Technology, scheduled to be launched na Q4 2017.

    \item \textbf{Engineering model} -- This model is form, fit, and functionally the same as the final flight model; however, it will use a mixture of flight-grade components (usually spare or out-of-life in stores) and commercial components. \cite{Models_space}

    \item \textbf{Qualification model} -- This is the model that is subjected to the qualification campaign. This usually includes design updates from the EM and uses identical components to flight; however, these components do not need to be screened to the flight standard. \cite{Models_space}

    \item \textbf{Flight model} -- The models actually flying; these are tested to acceptance-level testing. \cite{Models_space}

    \item \textbf{COTS} --  Components which are adapted to satisfy the needs of the purchasing organization, rather than the commissioning of custom made solutions, especially in high-reliability designs.

\end{itemize}

\section{Abbreviations}
\begin{itemize}
    \item    \textbf{ADC}      --    Analog to Digital Converter
    \item    \textbf{API}      --    Application Programming Interface
    \item    \textbf{ASIC}     --    Application Specific Integrated Circuit
    \item    \textbf{COTS}     --    Commercial Off-The-Shelf
    \item    \textbf{DC}       --    Direct Current
    \item    \textbf{DUT}      --    Device Under Test
    \item    \textbf{ECSS}     --    European Cooperation for Space Standardization
    \item    \textbf{EMC}      --    Electromagnetic Compatibility
    \item    \textbf{EMI}      --    Electromagnetic Interference
    \item    \textbf{EPS}      --    Electrical Power Supply
    \item    \textbf{ESCIES}   --    European Space Components Information Exchange System
    \item    \textbf{ESD}      --    Electrostatic Discharge
    \item    \textbf{FDIR}     --    Fault Detection, Isolation and Recovery
    \item    \textbf{GPIO}     --    General Purpose Input Output
    \item    \textbf{HAL}      --    Hardware Abstraction Layer
    \item    \textbf{$I^2C$}   --    Inter-Integrated Circuit
    \item    \textbf{I/O}      --    Input/Output
    \item    \textbf{LCL}      --    Latch-up Current Limiter
    \item    \textbf{LDO}      --    Low-Dropout linear regulator
    \item    \textbf{LEO}      --    Low Earth Orbit
    \item    \textbf{LET}      --    Linear Energy Transfer
    \item    \textbf{LSB}      --    Least Significant Bit
    \item    \textbf{LTAN}     --    Local Time Ascending Node
    \item    \textbf{MCU}      --    Micro-Controller Unit
    \item    \textbf{MOSFET}   --    Metal–Oxide–Semiconductor Field-Effect Transistor
    \item    \textbf{MUX}      --    Multiplexer
    \item    \textbf{OBC}      --    On-Board Computer
    \item    \textbf{PCB}      --    Printed Circuit Board
    \item    \textbf{PLD}      --    Payload
    \item    \textbf{PSRR}     --    Power supply rejection ratio
    \item    \textbf{RF}       --    Radio Frequencies
    \item    \textbf{RMS}      --    Root-Mean Squared
    \item    \textbf{RadFET}   --    Radiation Sensitive Field Effect Transistor
    \item    \textbf{SAA}      --    South Atlantic Anomaly
    \item    \textbf{SEE}      --    Single Event Effect
    \item    \textbf{SEL}      --    Single Event Latch-up
    \item    \textbf{SEU}      --    Single Event Upset
    \item    \textbf{SMD}      --    Surface Mounted Device
    \item    \textbf{TID}      --    Total Ionizing Dose
    \item    \textbf{ZTC}      --    Zero    Temperature    Coefficient
\end{itemize}
