\chapter{Engineering model}
This chapter will describe engineering model developed during this thesis.

This model should be as close to flight model as possible - but it could be e.g. on separate board, which is this case.

This model was developed as flight-ready version for sensor calibration \& tests along with developing \& testing flight software.

\section{Background - calibration stand}
    During development of the system previous model was developed to test and calibrate MOSFET transistors to use as a radiation dosimeters. Calibration stand was developed by M. Gumiela in his engineering thesis \cite{MGThesis}. The basic goal was to develop measurement device which can be used to determine final operational point, calibrate radiation response and to perform temperature calibration of flight sensor.

    TODO: opis stanowiska


\section{Block diagram}
    Block diagram of proposed system based on CD4007 is presented on figure TODO.

    It was designed having in mind miniaturization of sensor - to fit on PW-Sat2 PLD board. Because CD4007 has 3 complementary MOS pairs it was proposed to use all of them - to improve fidelity of the measurements. One n-MOS is used as a temperature sensor.

    Current source and ADC are multiplexed between 4 channels - 3x p-MOS and 1x n-MOS. This reduces board space and sensor accuracy (1 current source/ADC can be more sophisticated).

\section{Low-level requirements}
    Using design requirements \ref{Design_requirements} and characteristic curves from \ref{Characteristic_curves} low-level specifications were assumed:
    \begin{itemize}
        \item operating temperature range: $0 \div 60 \si{\degreeCelsius}$,
        \item current source value: $\SI{100}{\micro\ampere} \pm \SI{10}{\nano\ampere}$,
        \item ADC resolution: $TODO$,
        \item ADC accuracy: $TODO$,
        \item Noise floor on ADC: $TODO$
    \end{itemize}

\section{Analog front-end}
    \subsection{Current source}
    \subsection{ADC}
    \subsection{Multiplexer}
    \subsection{LDO}
    \subsection{Shielding}

\section{Digital}
    \subsection{Microcontroller}
    \subsection{OBC interface}

\section{Software design}
    \subsection{AVR-HAL}
    \subsection{I2C-slave module}
    \subsection{Measurement algorithm}

\section{PCB}
    \subsection{PCB stack}
    \subsection{PCB layout}
    \subsection{3D model}
    \subsection{Manufacturing}

\section{Assembly}

\section{Finished sensor}
