\chapter{Summary}
    The engineering model of the sensor was designed and preliminarily tested. This is a solid foundation to further work, which will result in the flight-ready version of the sensor. This model allowed for testing of the concept and possible solutions of sensor components, proving the design.

    Tests have proven the fidelity of measurements - assumed resolution and range are beyond the requirements. Designed sensor parameters are shown in table \ref{sensor_results_parameters}.

    \begin{table}[H]
        \caption{Finished sensor parameters}
        \label{sensor_results_parameters}
        \begin{center}
            \begin{tabular}{r|l}
                \textbf{Parameter} & \textbf{Result} \\ \hline
                Sensor resolution & \SI{0.003}{\rad}, \\
                Sensor accuracy & \SI{1}{\rad}, \\
                Sensor range & \SI{10}{\kilo\rad}, \\
                Operating temperature range & \SI{0}{\degreeCelsius} to \SI{70}{\degreeCelsius}, \\
                Communication protocol & $I^2C$, \\
                Sensor supply voltage & \SI{5}{\volt}, \\
                Sensor power consumption & \SI{0.125}{\watt}, \\
                Radiation tolerance & $>~\SI{15}{\kilo\rad}$ \\

            \end{tabular}
        \end{center}
    \end{table}

    This thesis resulted in a fully integrated, ready to use sensor which can be used as a preliminary calibration check model. It was designed for a space environment, with the limitations and requirements of CubeSat satellite in mind. During testing, the sensor design was proved through the conduction of tests. Moreover, since its size and requirements on the bus have been limited, broader possibilities of manufacturing this sensor as a separate module exist for other CubeSat missions.

    As a next step, this model has to be tested more throughly - especially radiation tests and calibration. Later, qualification and flight models will be manufactured, hopefully leading to sensor launch on PW-Sat2 satellite at the end of year 2017, where it can be tested in target space conditions.
